\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-05-05 draft.tex
add reference to Roemer 1997 about probabilistic voting; closes #19

Alternatively, the integration of the random variable $\ta$ can represent reduced-form modeling of political uncertainty arising from a complex decision-making process within a legislature. One can interpret $\ta$ as measuring uncertainty over the identity of the median legislator in order to represent the idea that the lobbying and voting ``game'' that goes on within legislatures is often complex enough that none of the actors know precisely what the outcome will be---that is, no one can predict exactly which legislator will be the median and therefore what weight will be placed on import-industry profits at the time of the vote. Thus one way we can think about $\ta$ is as an additional influence on the legislature's preferences about which all parties---executives, legislators and lobbies alike---are uncertain. It is this interpretation of $\ta$ I take throughout this paper. %need to keep this paragraph and the next, or at least parts of it, to satisfy #22

@@

>>>>

Alternatively, the integration of the random variable $\ta$ can represent reduced-form modeling of political uncertainty arising from a complex decision-making process within a legislature. One can interpret $\ta$ as measuring uncertainty over the identity of the median legislator. \textbf{In this sense, the idea is similar to that of the probabilistic voting models that incorporate policy motivation such as Roemer (1997).} Here, it is meant to represent the idea that the lobbying and voting ``game'' that goes on within legislatures is often complex enough that none of the actors know precisely what the outcome will be---that is, no one can predict exactly which legislator will be the median and therefore what weight will be placed on import-industry profits at the time of the vote. Thus one way we can think about $\ta$ is as an additional influence on the legislature's preferences about which all parties---executives, legislators and lobbies alike---are uncertain. It is this interpretation of $\ta$ I take throughout this paper. %need to keep this paragraph and the next, or at least parts of it, to satisfy #22

@@

\item \textbf{Roemer, J., 1997. Political-economic Equilibrium when Parties Represent Constituents: The Unidimensional Case. Social Choice and Welfare 14, 479-502.}

### 2016-05-05 letter-round2.tex
add reference to Roemer 1997 about probabilistic voting; closes #19

\vskip.3in
Some comments on substance, chronologically:
\begin{itemize}
\renewcommand\labelitemi{-}
	\item \textit{Assuming that lobbies represent only import-competing interests is a strong assumption and it requires theoretical and/or empirical justification.} \\
	Done, on page [8]
	\item \textit{Your model is static, so claiming that it rationalizes the four-year delay and eventual ratification of the US-SK FTA is a stretch. In particular, the interactions with automakers suggests a that a bargaining game under incomplete information would be more appropriate.} \\
	I have removed this claim.
  \item \textit{Your assumption that the identity of the median voter is not known a priori is standard in probability voting models, so you may want to stress the analogy between your setting and such models.}
  \item \textit{You claim that trade agreements act as a domestic political commitment device. To make this point formally, it would be nice to establish conditions under which, in equilibrium, ``fast track authority'' dominates cherry picking ex ante (in a version of your model with several import competing sectors).} \\
		I believe that I have already made this point formally in Result 3. The proof invokes Result 2 and Lemma 3 as it combines both dynamics that are explained intuitively in the text. I have made this more explicit by referring to those results in the text.

@@

	Alternatively, I can make an assumption on the support of $\theta$ and the functional form of $\ga$ so that Assumption 3 becomes a result, but this seems overly restrictive to make the points of the paper.

>>>>

\vskip.3in
Some comments on substance, chronologically:
\begin{itemize}
\renewcommand\labelitemi{-}
	\item \textit{Assuming that lobbies represent only import-competing interests is a strong assumption and it requires theoretical and/or empirical justification.} \\
	Done, on page [8]
	\item \textit{Your model is static, so claiming that it rationalizes the four-year delay and eventual ratification of the US-SK FTA is a stretch. In particular, the interactions with automakers suggests a that a bargaining game under incomplete information would be more appropriate.} \\
	I have removed this claim.
  \item \textit{Your assumption that the identity of the median voter is not known a priori is standard in probability voting models, so you may want to stress the analogy between your setting and such models.} \\
	Thank you for this suggestion. I have incorporated a short reference on page [ ].

  \item \textit{You claim that trade agreements act as a domestic political commitment device. To make this point formally, it would be nice to establish conditions under which, in equilibrium, ``fast track authority'' dominates cherry picking ex ante (in a version of your model with several import competing sectors).} \\
		I believe that I have already made this point formally in Result 3. The proof invokes Result 2 and Lemma 3 as it combines both dynamics that are explained intuitively in the text. I have made this more explicit by referring to those results in the text.

@@

	Alternatively, I can make an assumption on the support of $\theta$ and the functional form of $\gamma$ so that Assumption 3 becomes a result, but this seems overly restrictive to make the points of the paper.
